\documentclass[11pt,letterpaper,onecolumn,onepage]{wilson}

\title{}
\author{}
\date{}
\shortdate{}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.1cm}

\pagenumbering{gobble}

\begin{document}
	\begin{center}
		\textbf{CONSENT TO PARTICIPATE IN A RESEARCH STUDY}
	\end{center}
	
	\textbf{Title of Study}: Internet-based psycholinguistic questionnaires
	
	\textbf{Principal Investigator(s)}: Michael Wilson, Brian Dillon
	
	\textbf{This study is funded by the University of Massachusetts Amherst.}
	
	Important aspects of the study you should know about:
	\begin{itemize}
		\item \textbf{\varul{Purpose}}: The purpose of the study is to investigate the processes involved in the comprehension of sentences. The information collected in this study will be used in the preparation of papers for presentation in international conferences and journals on language.
    	\item \textbf{\varul{Procedures}}: If you choose to participate, you may first be asked to answer a few questions about your language background, and then you will be asked to read sentences. You may read sentences in a word-by-word fashion, or all at once. After you read the sentences, you will be asked a question or questions about the sentences, such as how natural they seem, or what you take to be the most likely meaning of the sentences.
    	\item \textbf{\varul{Duration}}: This will take about 30 to 45 minutes.
    	\item \textbf{\varul{Risks}}: There are no known risks involved in this experimental procedure. However, with any online research there is a minimal risk of breach of confidentiality. To guard against this possibility, we will not collect any uniquely identifying information on the servers where our data are collected. Your results will be kept confidential to the best of our ability. Your name will not appear in any publication or presentation. To maximize confidentiality, your results will be assigned to a subject identifier even for our own analyses, and information linking you to your data will be kept confidential or discarded.
    	\item \textbf{\varul{Benefits}}: You will receive no immediate personal benefits from your participation in this research other than your compensation.
    	\item \textbf{\varul{Costs and Compensation}}: If you decide to participate in this study, you will be compensated at a rate of 15 USD per hour.
    	\item \textbf{\varul{Participation}}: Taking part or not in this research study is your decision. You do not have to provide any information you are not comfortable providing. You can decide to participate and then change your mind at any point, though note that doing so means you agree to forfeit compensation.
	\end{itemize}
	
	\textbf{\varul{Contact information}}: If you have any questions about the purpose, procedures, or any other issues related to this research study you may contact the Principle Investigators: Dr. Michael Wilson at \href{mailto:mawilson@udel.edu}{\textcolor{delblue}{\varul{mawilson@udel.edu}}}, or Dr. Brian Dillon at \href{mailto:bwdillon@umass.edu}{\textcolor{delblue}{\varul{bwdillon@umass.edu}}}. If you would like to speak with someone not directly involved in the research study, you may contact the Chair of the Linguistics \& Cognitive Science Department of the University of Delaware, Dr. Robin Andreasen, at \href{mailto:robina@udel.edu}{\textcolor{delblue}{\varul{robina@udel.edu}}}. You may also contact the University of Delaware Research Office at (302) 831-2136, or the University of Massachusetts Amherst Human Research Protection Office at (413) 545-3428.\\
	
	\textbf{\textsc{consent to participate in the research study}:}
	
	\textbf{I have read and understood the information in this form and I agree to participate in the study. I am 18 years of age or older. I have been given the opportunity to ask any questions I had and those questions have been answered to my satisifaction. I understand that I may save a copy of this webpage for my records. I understand the purpose of the research, the study procedures that I will undergo, and the possible risks and discomforts as well as benefits that I may experience. I have read and understood these terms of consent. Therefore, I agree to give my consent to participate as a subject in this research project.}
\end{document}